\documentclass[letterpaper]{book}
\usepackage[times,inconsolata,hyper]{Rd}
\usepackage{makeidx}
\usepackage[utf8]{inputenc} % @SET ENCODING@
% \usepackage{graphicx} % @USE GRAPHICX@
\makeindex{}
\begin{document}
\chapter*{}
\begin{center}
{\textbf{\huge Package `IsoplotR'}}
\par\bigskip{\large \today}
\end{center}
\begin{description}
\raggedright{}
\inputencoding{utf8}
\item[Title]\AsIs{Statistical Toolbox for Radiometric Geochronology}
\item[Version]\AsIs{3.0}
\item[Date]\AsIs{2019-08-01}
\item[Description]\AsIs{Plots U-Pb data on Wetherill and Tera-Wasserburg concordia diagrams. Calculates concordia and discordia ages. Performs linear regression of measurements with correlated errors using 'York', 'Titterington' and 'Ludwig' approaches. Generates Kernel Density Estimates (KDEs) and Cumulative Age Distributions (CADs). Produces Multidimensional Scaling (MDS) configurations and Shepard plots of multi-sample detrital datasets using the Kolmogorov-Smirnov distance as a dissimilarity measure. Calculates 40Ar/39Ar ages, isochrons, and age spectra. Computes weighted means accounting for overdispersion. Calculates U-Th-He (single grain and central) ages, logratio plots and ternary diagrams. Processes fission track data using the external detector method and LA-ICP-MS, calculates central ages and plots fission track and other data on radial (a.k.a. 'Galbraith') plots. Constructs total Pb-U, Pb-Pb, K-Ca, Re-Os, Sm-Nd, Lu-Hf, Rb-Sr and 230Th-U isochrons as well as 230Th-U evolution plots.}
\item[Author]\AsIs{Pieter Vermeesch [aut, cre]}
\item[Maintainer]\AsIs{Pieter Vermeesch }\email{p.vermeesch@ucl.ac.uk}\AsIs{}
\item[Depends]\AsIs{R (>= 3.0.0)}
\item[Imports]\AsIs{MASS, grDevices, graphics, stats, utils}
\item[License]\AsIs{GPL-3}
\item[URL]\AsIs{}\url{http://isoplotr.london-geochron.com}\AsIs{}
\item[LazyData]\AsIs{true}
\item[RoxygenNote]\AsIs{6.1.1}
\item[Encoding]\AsIs{UTF-8}
\end{description}
\Rdcontents{\R{} topics documented:}
